---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load_data, echo=TRUE}
act <- read.csv(unz("activity.zip","activity.csv") )
act$date <- as.Date(act$date)
summary(act)
str(act)
```


## What is mean total number of steps taken per day?
```{r steps_per_day, echo=TRUE}
act_day <- aggregate( steps ~ date  , data = act ,FUN = "sum",na.rm= TRUE)
act_day_mean <- formatC(mean(act_day$steps),format = "f",digits  = 2,big.mark = ",")
act_day_median <- formatC(median(act_day$steps),format = "f", digits = 2, big.mark = ",")
hist(act_day$steps,breaks = 10, main = "Histogram of total number of steps taken per day", 
     xlab = "steps per day")
```

Mean of total number of steps is **`r act_day_mean`**.
Median of total number of steps is **`r act_day_median`**. 

## What is the average daily activity pattern?
```{r steps_interval, echo=TRUE}
act_interval <- aggregate( steps ~ interval  , data = act ,FUN = "mean")
act_interval_max <- act_interval[act_interval$steps == max(act_interval$steps),]$interval
plot(act_interval$interval, act_interval$steps,type = "l",
     xlab = "5-minute interval",ylab = "Average number of steps taken, averaged across all days", 
     main = "Average number of steps taken,\naveraged across all days of 5-minute interval")
```
5-minute interval with maximun number of average step across all days is  **`r act_interval_max`**.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
