---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load_data, echo=TRUE}
act <- read.csv(unz("activity.zip","activity.csv") )
act$date <- as.Date(act$date)
```


## What is mean total number of steps taken per day?
```{r steps_per_day, echo=TRUE}
act_day <- aggregate( steps ~ date  , data = act ,FUN = "sum",na.rm= TRUE)
hist(act_day$steps,breaks = 50, main = "Histogram of total number of steps taken per day", 
     xlab = "steps per day")
```

Mean of total number of steps is **`r formatC(mean(act_day$steps),format = "f",digits  = 2,big.mark = ",")`**.
Median of total number of steps is **`r formatC(median(act_day$steps),format = "f", digits = 2, big.mark = ",")`**. 

## What is the average daily activity pattern?
```{r steps_interval, echo=TRUE}
act_interval <- aggregate( steps ~ interval  , data = act ,FUN = "mean")
plot(act_interval$interval, act_interval$steps,type = "l",
     xlab = "5-minute interval",ylab = "Average number of steps taken, averaged across all days", 
     main = "Average number of steps taken,\naveraged across all days of 5-minute interval")
```  

5-minute interval with maximun number of average step across all days is  **`r act_interval[act_interval$steps == max(act_interval$steps),]$interval`**.

## Imputing missing values

Total number of rows with NAs is **`r nrow(act[is.na(act$steps),])`**.  
Filling the missing value in dataset with ***mean of each 5-minute interval***by the code belows, because there are all NAs on some day.

```{r imput_na, echo=TRUE}
act_nafilled <- act

for(interval in unique(act_nafilled$interval)){
  act_nafilled[ is.na(act_nafilled[,1]) & act_nafilled[,3]==interval,1] <- 
    mean(act_nafilled[act_nafilled[,3]==interval,1],na.rm = TRUE)
}


act_nona_day <- aggregate( steps ~ date  , data = act_nafilled ,FUN = "sum")
hist(act_nona_day$steps,breaks = 50, main = "Histogram of total number of steps taken per day (with filling NAs)",xlab = "steps per day")

```

Mean of total number of steps is **`r formatC(mean(act_nona_day$steps),format = "f",digits  = 2,big.mark = ",")`**.
Median of total number of steps is **`r formatC(median(act_nona_day$steps),format = "f", digits = 2, big.mark = ",")`**. 
From this filling strategy, imputing missing data impact on ***median value***. Median of total number of steps is adjusted to equal mean value.

## Are there differences in activity patterns between weekdays and weekends?
```{r weekday_end_diff, echo=TRUE}
act_nafilled$weekday <- "weekday"
#เสาร์ อาทิตย์ is Thai weekends.
act_nafilled[ weekdays(act_nafilled$date) %in% c("เสาร์","อาทิตย์"),]$weekday <- "weekend"
act_nafilled$weekday <- as.factor(act_nafilled$weekday)

act_nafilled_avg <- aggregate( steps ~ interval + weekday   , data = act_nafilled ,FUN = "mean",na.rm= TRUE)

library(lattice) 
xyplot(steps~interval|weekday, 
   data = act_nafilled_avg,
   layout = c(1,2),
   xlab="Interval", ylab="Number of steps",
   type="l",
   main="Activity patterns between weekdays and weekends") 

```

Activity in weekends is lower than weekdays, except activity, around interval 800, is higher.
